Sr: Processing Data Streams By Doing Less Work

### 2012-05-03 paper/paper.tex
Baller tables

\usepackage{fullpage}
\usepackage{listings}
\usepackage{graphicx}
\graphicspath{{images/}}

@@

\begin{table}
\begin{tabular}{|l|p{5cm}|}
 \hline
Weight & Description \\ \hline
1.0 & Deflate and decode fulltext and count words in all of fulltext \\ \hline
0.25 & Deflate and decode fulltext and count words in approximately a quarter of fulltext \\ \hline
0.1 & Return the results of the last computation from a cache \\ \hline
\end{tabular}
\caption{Computation routines used by Sr workers}
\label{table:workerTasks}
\end{table}

@@

\subsubsection{Word Count Job Accuracy}
Because I am running a top-k job, I compute the $F_{0.5}$-score of the Sr results as opposed to the $F1$-score because I care more about precision of the top k than recall in the tail. Figure ~\ref{fig:fscore} shows that the $F_{0.5}$-score, or the weighted accuracy of the top-100 classifier, is always higher than the fraction of the input examined (kill rate * work level).

@@

\begin{table}
\begin{tabular}{|l|l|l|}
\hline
Kill rate & Work level & Avg. execution time \\ \hline
0.0 & 1.0 & 11:35.5 \\ \hline
0.0 & 0.4 & 10:33.8 \\ \hline
0.0 & 0.8 & 10:30.8 \\ \hline
0.2 & 0.4 & 08:25.8 \\ \hline
0.2 & 0.8 & 08:37.8 \\ \hline
0.4 & 0.4 & 06:54.0 \\ \hline
0.4 & 0.8 & 06:28.2 \\ \hline
0.6 & 0.4 & 04:14.7 \\ \hline
0.6 & 0.8 & 04:13.7 \\ \hline
0.8 & 0.4 & 02:33.3 \\ \hline
0.8 & 0.8 & 02:15.0 \\ \hline
\end{tabular}
\caption{Impact of Kill rate and work level on job execution time}
\label{table:runtime}
\end{table}

@@

\section{Discussion}

\section{Conclusion}

\section{Acknowledgements}

\section{References}

>>>>

\usepackage{fullpage}
\usepackage{listings}
\usepackage{graphicx}
\graphicspath{{images/}}
\usepackage{tabularx}

@@

\begin{table}
\begin{tabularx}{\linewidth}{|c|X|}
 \hline
Weight & Description \\ \hline
1.0 & Deflate and decode fulltext and count words in all of fulltext \\ \hline
0.25 & Deflate and decode fulltext and count words in approximately a quarter of fulltext \\ \hline
0.1 & Return the results of the last computation from a cache \\ \hline
\end{tabularx}
\caption{Computation routines used by Sr workers}
\label{table:workerTasks}
\end{table}

@@

\subsubsection{Word Count Job Accuracy}
Because I am running a top-k job, I compute the $F_{0.5}$-score of the Sr results as opposed to the $F1$-score because I care more about precision of the top k than recall in the tail. Figure ~\ref{fig:fscore} shows that the $F_{0.5}$-score, or the weighted accuracy of the top-100 classifier, is always higher than the fraction of the input examined (kill rate * work level). Setting the work level to 0.4 nets a greater increase in job accuracy versus fraction of words examined, with accuracy approximately 1.75 times more than the fraction of words examined.

@@

\begin{table}
\begin{tabularx}{\linewidth}{|X|X|X|}
\hline
Kill rate & Work level & Avg. execution time [minutes] \\ \hline
0.0 & 1.0 & 11:35.5 \\ \hline
0.0 & 0.4 & 10:33.8 \\ \hline
0.0 & 0.8 & 10:30.8 \\ \hline
0.2 & 0.4 & 08:25.8 \\ \hline
0.2 & 0.8 & 08:37.8 \\ \hline
0.4 & 0.4 & 06:54.0 \\ \hline
0.4 & 0.8 & 06:28.2 \\ \hline
0.6 & 0.4 & 04:14.7 \\ \hline
0.6 & 0.8 & 04:13.7 \\ \hline
0.8 & 0.4 & 02:33.3 \\ \hline
0.8 & 0.8 & 02:15.0 \\ \hline
\end{tabularx}
\caption{Impact of kill rate and work level on job execution time.}
\label{table:runtime}
\end{table}

@@
